### 2017-02-03 paper/chapters/vae/cvae.tex
improve iwae citation (in title, oops)

Instead of using VAEs in a completely unsupervised manner on a unlabeled dataset, it is also possible to learn from datasets where a small subset of datapoints has corresponding labels while most datapoints are still unlabeled.
Techniques learning from such datasets are called semi-supervised learning and can improve performance significantly.\\

To adjust the VAE model to the semi-supervised case, we have to add an random variable $y$ corresponding to the corresponding label if available.
Thus we can extend the distributions as shown below.

>>>>

\todo[inline]{Add citations to \cite{cvae:2014} and \cite{cvae_2:2015}}
Instead of using VAEs in a completely unsupervised manner on a unlabeled dataset, it is also possible to learn from datasets where a small subset of datapoints has corresponding labels while most datapoints are still unlabeled.
Techniques learning from such datasets are called semi-supervised learning and can improve performance significantly.\\

To adjust the VAE model to the semi-supervised case, we have to add a random variable $y$ corresponding to the label if available.
Thus we can extend the distributions as shown below.
